### 2014-02-27 paper/concrete.tex
minor tweaks.

\Red{In this section I only talk about TSNI.  Once we finish the previous
  section to both talk about TSNI and TINI, we should do the same here.}

@@

We give the proof of this in Section~\ref{sec:proofs}.
Going back to our single-heap ML-like IFC language, we can
show that it is in fact NPRI, and thus non-interfering.

@@

\Red{Adapt proofs.}

>>>>

@@

Before we give the proof of this theorem in Section~\ref{sec:proofs},
let's consider our single-heap ML-like IFC language and
show that it is in fact NPRI, and thus non-interfering.

@@

\Red{Adapt the following proofs.}
